DATA 621 - Business Analytics and Data Mining

### 2020-11-24 HW5/HW5-Draft.Rmd
Poisson 2 & MLR 1 added

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #5'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg,
    Bryan Persaud, Jeff Shamp
date: "11/22/2020"
output:
  pdf_document:
  toc: TRUE
toc_depth: 4
urlcolor: purple
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(data.table)

@@

# ASSIGNMENT
The assignment for HW5 is to analyze and model a dataset containing
approximately 12,000 records representing commercially available wines. The
`TARGET` response variable represents the number of sample cases of wine
purchased by wine distribution companies after sampling that wine. These cases
would be used to provide tasting samples to restaurants and wine stores around
the United States. The more sample cases purchased, the more likely is a wine to
be sold at a high end restaurant.A large wine manufacturer is studying the data
in order to predict the number of wine cases ordered based upon the wine
characteristics. If the wine manufacturer can predict the number of cases, then
that manufacturer will be able to adjust their wine offering to maximize sales.

@@

|VARIABLE NAME|DEFINITION|THEORETICAL EFFECT|
|--|--|--|
|INDEX|Identification Variable (do not use)|None|
|TARGET|Number of Cases Purchased|None|
|AcidIndex|Proprietary method of testing total acidity of wine by using a weighted average||
|Alcohol|Alcohol Content||
|Chlorides|Chloride content of wine||
|CitricAcid|Citric Acid Content||
|Density|Density of Wine||
|FixedAcidity|Fixed Acidity of Wine||
|FreeSulfurDioxide|Sulfur Dioxide content of wine||
|LabelAppeal|Marketing Score indicating the appeal of label design for consumers. High numbers suggest customers like the label design. Negative numbers suggest customers don't like the design.|Many consumers purchase based on the visual appeal of the wine label design. Higher numbers suggest better sales.|
|ResidualSugar|Residual Sugar of wine||
|STARS|Wine rating by a team of experts. 4 Stars = Excellent, 1 Star = Poor|A high number of stars suggests high sales|
|Sulphates|Sulfate content of wine||
|TotalSulfurDioxide|Total Sulfur Dioxide of Wine||
|VolatileAcidity|Volatile Acid content of wine||
|pH|pH of wine||

@@

```{r targetH, fig.height=2, fig.width=3}
# Plot distribution of TARGET
ggplot(DT[, .(TARGET)], aes(x = TARGET)) +
  geom_histogram(binwidth = FDbin, fill = 'darkolivegreen4')
```

@@

## Poisson Model 1 & Negative Binomial Model 1
### Missing Data
The missing data can be split into two groups: `STARS` and the rest. For all the
others, I do not think there is signal encoded in the "missingness" and thus
will use some form of imputation. `STARS` is different as discussed in the DATA
EXPLORATION section. Therefore, I will create a new feature called `Rated` which
will be true if `STARS` is missing, and then only use this variable and its
interaction with `STARS` in the model, and not `STARS` by itself.

@@

# BUILD MODELS
## Poisson Model 1 & Negative Binomial Model 1
The same person is building these two models, and the model setups will be
similar. Each model will follow a similar format, with only the family changing.
Each will start with the saturated model including all the individual predictors
***except*** for `STARS`. There will also be the following interactions:

  * `Rated` and `STARS`
    * As discussed above, by having `Rating` on its own and this interaction
    the effect of both having a rating and the effect of the rating level can be
    measured, without penalizing unrated wines a second time for a 0.
  * The full four-way interaction between `AcidIndex`, `FixedAcidity`,
  `VolatileAcidity`, and `pH`
    * There are **four** separate predictors relating to acidity. Despite their
    Pearson product-moment correlations being low, I am suspicious of too much
    weight being given to acidity. By including their interactions, effects can
    be tempered, or magnified, as necessary. `CitricAcid` is not included here
    as is not merely an acid but a flavor provider as well. Also, five-way
    interactions lead to migraines.
  * `FreeSulfurDioxide` and `TotalSulfurDioxide`
    * Again, a case of multiple theoretically related predictors
  * `LabelAppeal` with `Rated` and `LabelAppeal` with `Rated:STARS`
    * This is a later addition. The top three predictors in magnitude were
    `LabelAppeal`, `Rated`, and `Rated:STARS`. With all three being so strong,
    there may be interactions between them. However, as `STARS` alone has been
    removed from contention, only the interactions between the two others will
    be considered.

@@

## Poisson Model #2

## Negative Binomial Model #2

## Multiple Linear Regrssion Model # 1

## Multiple Linear Regrssion Model # 2

@@

### Negative Binomial Model 1
```{r m1NBTest}
# NB1: Test Model
m1NBtstPred <- round(predict(m1NBFit, newdata = m1tstImp))
compTable[3, 2] <- m1NBRMSE <- RMSE(m1NBtstPred, m1tstImp$TARGET)
compTable[3, 3] <- m1NBMAE <- MAE(m1NBtstPred, m1tstImp$TARGET)
compTable[3, 4] <- m1NBFitAIC
```

@@

@@

@@

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
<!-- Assignment -->
```{r loadData}
```
<!-- Data Exploration -->
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
<!-- Data Preparation -->
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
<!-- Build Models -->
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
```{r m1PvarImp}
```
```{r m1NBTrain}
```
```{r m1NBTable}
```
```{r m1NBvarImp}
```
```{r m1PNB}
```
<!-- Other prep and build goes here -->
<!-- Select Models -->
```{r compTable}
```
```{r m1TestProcess}
```
```{r m1PTest}
```
<!-- Poisson 2 Test goes here -->
```{r m1NBTest}
```
<!-- Remaining Test sets go here -->
```{r modelTestResults}
```

>>>>

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #5'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg,
    Bryan Persaud, Jeff Shamp
date: "11/28/2020"
output:
  pdf_document:
    toc: TRUE
    toc_depth: 4
urlcolor: purple
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(data.table)
library(mice)
library(pscl)
library(mpath)
library(dplyr)

@@

# ASSIGNMENT
The assignment for HW5 is to analyze and model a dataset containing
approximately 12,000 records representing commercially available wines. The
`TARGET` response variable represents the number of sample cases of wine
purchased by wine distribution companies after sampling that wine. These cases
would be used to provide tasting samples to restaurants and wine stores around
the United States. The more sample cases purchased, the more likely is a wine to
be sold at a high end restaurant. A large wine manufacturer is studying the data
in order to predict the number of wine cases ordered based upon the wine
characteristics. If the wine manufacturer can predict the number of cases, then
that manufacturer will be able to adjust their wine offering to maximize sales.

@@

|VARIABLE NAME|DEFINITION|THEORETICAL EFFECT|
|--|----|---|
|INDEX|Identification Variable (do not use)|None|
|TARGET|Number of Cases Purchased|None|
|AcidIndex|Proprietary method of testing total acidity of wine by using a weighted average||
|Alcohol|Alcohol Content||
|Chlorides|Chloride content of wine||
|CitricAcid|Citric Acid Content||
|Density|Density of Wine||
|FixedAcidity|Fixed Acidity of Wine||
|FreeSulfurDioxide|Sulfur Dioxide content of wine||
|LabelAppeal|Marketing Score indicating the appeal of label design for consumers. High numbers suggest customers like the label design. Negative numbers suggest customers don't like the design.|Many consumers purchase based on the visual appeal of the wine label design. Higher numbers suggest better sales.|
|ResidualSugar|Residual Sugar of wine||
|STARS|Wine rating by a team of experts. 4 Stars = Excellent, 1 Star = Poor|A high number of stars suggests high sales|
|Sulphates|Sulfate content of wine||
|TotalSulfurDioxide|Total Sulfur Dioxide of Wine||
|VolatileAcidity|Volatile Acid content of wine||
|pH|pH of wine||

@@

```{r targetH, fig.height=2, fig.width=3, fig.align='center'}
# Plot distribution of TARGET
ggplot(DT[, .(TARGET)], aes(x = TARGET)) +
  geom_histogram(binwidth = FDbin, fill = 'darkolivegreen4')
```

@@

## Poisson Model #1 & Negative Binomial Model #1
### Missing Data
The missing data can be split into two groups: `STARS` and the rest. For all the
others, I do not think there is signal encoded in the "missingness" and thus
will use some form of imputation. `STARS` is different as discussed in the DATA
EXPLORATION section. Therefore, I will create a new feature called `Rated` which
will be true if `STARS` is missing, and then only use this variable and its
interaction with `STARS` in the model, and not `STARS` by itself.

@@

## Poisson Model #2 & Multiple Linear Regrssion Model #1

The right balance of the chemical properties of the wine is essential to make 
it tastes, looks, and smells delightful, in addition to having a long shelf-life.
Typically, citric acid and alcohol are the main positive attributes a wine 
should have, while volatile acidity and sulphates are the main negative ones. 
However, the dataset has negative values instead of near-zero in some of these 
variables describing the chemical properties of the wine. Because little is given 
about whether or not these variables were normalized, absolute values will be 
taken assuming there was an error made during data collection.

Lastly, to handle missing data for `STARS`, they will be replaced by 0, while 
the chemical properties will be imputed. Because the predictive mean matching 
imputation method combines the standard linear regression and the nearest-neighbor 
imputation approach, Model Set #2 elected to fill in missing values of a 
continuous variable by using it. Afterward, the data is pre-processed to fulfill 
the assumption of normality using the Yeo-Johnson transformation 
[(Yeo & Johnson, 2000)](https://www.jstor.org/stable/2673623?seq=1). This technique 
attempts to find the value of lambda that minimizes the Kullback-Leibler distance 
between the normal distribution and the transformed distribution. This method 
has the advantage of working without having to worry about the domain of x.

```{r m2clean}
set.seed(525)
m2train <- copy(trnSet[,-1])
m2train[,c(2:8,11:12)] <- abs(m2train[,c(2:8,11:12)])
m2train$STARS[is.na(m2train$STARS)] <- 0
m2train.impute <- mice(m2train, method = 'pmm', print = FALSE)
m2train <- complete(m2train.impute)
m2train.r <- m2train$TARGET
m2train.p <- m2train[,-1]
pre.process <- preProcess(m2train.p, method = c("YeoJohnson"))
m2train.p <- predict(pre.process, m2train.p)
m2train[,c(2:13,15)] <- m2train.p[,c(1:12,14)]
```

## Multiple Linear Regression #2 & Negative Binomial Model #2
### Missing Data
These models will deal with missing numerical data by imputing the NA's
using the Multivariate imputation by chained equations (MICE) method. Multiple
imputation involves creating multiple predictions for each missing value, helping 
to account for the uncertainty in the individual imputations.

```{r model3impute}
set.seed(123)
# ML2 & NB2 data transformation
# MICE imputation on train and test set
m3train <- complete(mice(data = trnSet %>% select(-INDEX),
                         method = "pmm", print = FALSE), 3)
m3test <- complete(mice(data = tstSet %>% select(-INDEX),
                        method = "pmm", print = FALSE), 3)
```

# BUILD MODELS
## Poisson Model #1 & Negative Binomial Model #1
The same person is building these two models, and the model setups will be
similar. Each model will follow a similar format, with only the family changing.
Each will start with the saturated model including all the individual predictors
***except*** for `STARS`. There will also be the following interactions:

  * `Rated` and `STARS`
    * As discussed above, by having `Rating` on its own and this interaction
    the effect of both having a rating and the effect of the rating level can be
    measured, without penalizing unrated wines a second time for a 0.
  * The full four-way interaction between `AcidIndex`, `FixedAcidity`,
  `VolatileAcidity`, and `pH`
    * There are **four** separate predictors relating to acidity. Despite their
    Pearson product-moment correlations being low, I am suspicious of too much
    weight being given to acidity. By including their interactions, effects can
    be tempered, or magnified, as necessary. `CitricAcid` is not included here
    as is not merely an acid but a flavor provider as well. Also, five-way
    interactions lead to migraines.
  * `FreeSulfurDioxide` and `TotalSulfurDioxide`
    * Again, a case of multiple theoretically related predictors.
  * `LabelAppeal` with `Rated` and `LabelAppeal` with `Rated:STARS`
    * This is a later addition. The top three predictors in magnitude were
    `LabelAppeal`, `Rated`, and `Rated:STARS`. With all three being so strong,
    there may be interactions between them. However, as `STARS` alone has been
    removed from contention, only the interactions between the two others will
    be considered.

@@

## Poisson Model #2 & Multiple Linear Regrssion Model #1
The `TARGET` variable has 2734 observations with zero values. This could be a result 
of the manufacturer not releasing the wine into the market, or that there were no 
orders placed. Therefore, backward stepwise variable elimination for a zero-inflated 
poisson (ZIP) analysis will be investigated to understand the conditions. This model is
further compared to the same Poisson model to determine whether there is an improvement.

In the ZIP model, the independent variable, $TARGET_i$, take zero values $TARGET_i \sim 0$ 
with the probability $\omega_i$ or values from Poisson distribution 
$TARGET_i \sim Pois(\lambda_i)$ with probability (1 - $\omega_i$). For $i = 1,..., n$, 
it can be written as:

\[P(Y_i = y_i) = \left\{\begin{matrix}\omega _i + (1-\omega_i)e^{-\lambda_i}), \text{ if } y_i = 0\\ (1-\omega_i)\frac{e^{-\lambda_i}\lambda_i^{y_i}}{y_i!},\text{ if } y_i > 0 \end{matrix}\right.\]

Therefore, the zero-inflated poisson model have two parameters, $\lambda_i$ and 
$\omega_i$, and linked with the predictor variables with the following:

\[log\left(\frac{\omega_i}{1-\omega_i}\right) = \sum_{j=1}^{t}\gamma_{ji}Z_{ji},\]

\[log\left(\lambda_i\right) = \sum_{j=1}^{k}\beta_{ji}X_{ji},\]

where $Z_1,..., Z_l$ are the dependent variables for the first equation and 
$X_1,..., X_k$ for the second one. The expected value and variance of the number 
of cases purchased for the $i^{th}$ wine in the ZIP model are, respectively:

\[E(Y_i) = \lambda_i(1 - \omega_i),\]

\[Var(Y_i) = (1 - \omega_i)(\lambda_i - \omega_i\lambda_i^2).\]

Similar to Poisson regression, the ZIP model assumes that the average number of 
cases purchased equals the variance. For more information, refer to 
[Zero-Inflated Poisson Regression](https://math.usu.edu/jrstevens/biostat/projects2013/rep_ZIP.pdf).

### Poisson Model #2

```{r m2poisson}
set.seed(525)
# Zero Inflated Poisson Model
m2.pmodel <- zeroinfl(TARGET~., 
                      dist = 'poisson', 
                      model = TRUE, 
                      data = m2train,
                      link = "logit")
# Backward Elimination
m2.fpmodel <- be.zeroinfl(m2.pmodel, 
                          data = m2train, 
                          dist = 'poisson', 
                          alpha = 0.05, 
                          trace = FALSE)
m2.poisson.aic <- AIC(m2.fpmodel)
```

Zero-inflated count models are two-component mixture models combining a point 
mass at zero with a proper count distribution. Thus, there are two sources of 
zeros: zeros may come from both the point mass and from the count component.

\small
```{r m2PTable}
kable(summary(m2.fpmodel)$coefficients$count,
      caption = "Zero Inflated Poisson Model #2 Count Output")
kable(summary(m2.fpmodel)$coefficients$zero,
      caption = "Zero Inflated Poisson Model #2 Zero Output")
```
\normalsize

```{r m2PFitCheck}
# Dispersion statistic
E2 <- resid(m2.fpmodel, type = "pearson")
N  <- nrow(m2train)
p  <- length(coef(m2.fpmodel))  
dp <- sum(E2^2) / (N - p)

# Poisson Model #2, same formula from ZIP model
m2.poisson <- glm(TARGET ~ Alcohol + LabelAppeal + AcidIndex + STARS | VolatileAcidity + 
                    CitricAcid + FreeSulfurDioxide + TotalSulfurDioxide + pH + 
                    Sulphates + Alcohol + LabelAppeal + AcidIndex + STARS, 
                  family = poisson(link = 'log'), data = m2train)
vuong(m2.poisson, m2.fpmodel)
```

This model has a dispersion parameter of `r prettyNum(dp, digits = 3L)` which 
suggests under-dispersion (i.e., variance < mean). This parameter indicates how 
many times larger the variance is than the mean. Since the dispersion was less 
than one, the conditional variance is smaller than the conditional mean. Models 
that ignore under-dispersion will be overly conservative and may fail to detect 
significant patterns. Generalized Poisson (GP) and Conway‐Maxwell‐Poisson (CMP)
distributions are better choices for such modeling because they can handle both 
over-dispersion and under-dispersion. But for the scope of this assignment, 
it's apparent, from the Vuong test with the same Poisson model and the ZIP model, 
that the zero-inflated Poisson model is a slight improvement over the Poisson 
model. Therefore, the ZIP model will still be considered among others.

#### Coefficient Discussion
All of the predictors in both the count and inflation portions of the model are 
statistically significant. This model fits the data significantly better than the 
null model, i.e., the intercept-only model. The count model contains information 
about variables that the parent Poisson model used to estimate `TARGET` on the 
condition that `TARGET` > 0. The coefficients for all 4 regression variables are 
statistically significant at a 99% confidence level. The coefficient for `AcidIndex`
is negative, meaning that as the total acidity of wine goes up by a unit, the number 
of purchased cases goes down by 2%. One the other hand, for the other variables, i.e. 
`Alcohol`, `LabelAppeal` and `STARS`, as these increase, the number of purchased 
cases will also increase. In particular, `LabelAppeal` can account for a 26% 
increase in the number of wine cases sold if the visual appeal of the wine 
scores increase by one unit and all other variables held constant. Whereas, there
is a 19% increase in cases sold for each increase in the wine rating by a team of 
experts, `STARS`.

The zero model contains information about variables that the nested Logistic 
Regression model has been used to estimate the probability of whether or not cases are
purchased. Examining the variables with a negative regression coefficient, this
suggests that as the factor for the specific chemical properties increases, the
probability of no case being purchase decreases. This is in line with our intuition,
particularly for the sulfur dioxide levels. When a wine has an unusually small 
percentage of the Free and Total $SO_2$, this suggests the wine is chemically and/or 
microbially unstable. Thus, if a wine manufacturer were to increase the sulfur 
dioxide levels by one unit, the odds that the wine would certainly not be purchased 
would decrease by a factor of 0.92 to 0.95. However, `LabelAppeal` is among the
positive coefficients for the zero model. This is interpreted as the higher a 
rating is for a bottle of wine, the more likely there will be no case purchase, and it
doesn't seem reasonable.

### Multiple Linear Regrssion Model #1

Multiple Linear Regression Model #1 will be using the step function has an options 
to use a process that both adds and removes variables in the model. It uses AIC 
(Akaike information criterion) as a selection criterion. A full model and a null 
are defined, and then the function will follow a procedure to find the model with 
the lowest AIC.

```{r m1MLRFit}
# Multiple Linear Regression model 
set.seed(525)
model.null = lm(TARGET ~ 1, data = m2train)
model.full = lm(TARGET ~ ., data = m2train)

# Step model used to derive final model, m1MLRFit  
# step(model.null,
#      scope = list(upper = model.full),
#      direction = "both",
#      data = m2train, 
#      trace = FALSE)

m1MLRFit = lm(TARGET ~ STARS + LabelAppeal + AcidIndex + TotalSulfurDioxide +
                VolatileAcidity + FreeSulfurDioxide + Alcohol + CitricAcid + 
                Chlorides + pH + Sulphates,
              data = m2train)
```

\small
```{r m1MLRTable}
kable(summary(m1MLRFit)$coefficient,
      caption = "Multiple Linear Regression Model #1 Output")
```
\normalsize

#### Coefficient Discussion
Contributing coefficients are those which lie within the 95% level of
significance. A positive coefficient indicates that as the value of the
predictor increases, the response variable also tends to increase. A negative
coefficient suggests that as the predictor increases, the response variable
tends to decrease.

The intercept itself suggests that with no other information about the wine,
there will be cases sold. The other positive predictors suggest that increasing
`STARS` and `LabelAppeal` will result in an increase in the number of case purchased. 
These make sense intuitively. Moreover, as discussed in the Poisson Model #2, the 
right balance of $SO_2$ lead to better wine, thus the coefficients are rather
small and have a smaller effect when it is increased. This reasoning is similar 
for `Alcohol` levels. Next, `CitricAcid`, commonly used as an acid supplement 
during fermentation, helps winemakers boost the acidity of their wine and 
stabilize ferric haze. So, it makes sense that the higher `CitricAcid` is, the
more cases would be sold. But once again, these need to be balance right.

On the contrary, an increase in a unit of volatile acidity results in the decrease
of case purchases. Volatile acidity is caused by bacteria or certain yeasts. This also
can increase the acid index and pH if it is high. This is why sulfur dioxide is used 
to carefully control it. In all, this model should not be taken as fixed, when it 
comes to chemical processes, the wine manufacturer needs to take care of what to
increase and decrease in order to reach equilibrium.

## Negative Binomial Model #2 & Multiple Linear Regrssion Model #2

### Negative Binomial Model #2
#### Baseline Model 
We will start with a simple negative binomial regression model to serve as a 
baseline. This includes all variables in the dataset.

```{r m2NBTrainBase}
m2NBBase <- glm.nb(TARGET ~ ., data = m3train)
knitr::kable(summary(m2NBBase)$coefficients, digits = 3L,
             caption = 'Negative Binomial Regression Model #2 - Base Output')
```
Immediately, we can see a few variables that do not meet the 0.05
p-value threshold.

#### Enhanced Model
Backwards stepwise regression is performed and the result is a model with the 
following variables *removed*: `FixedAcidity`, `CitricAcid`, `ResidualSugar`, 
and `Density`. Because the `Sulphates` variable is very close to the 0.05
p-value threshold of significance, we will remove it as well.

```{r m2NBTrain}
m2NBFit <- glm.nb(TARGET ~ VolatileAcidity + Chlorides +
                FreeSulfurDioxide + TotalSulfurDioxide + pH + Alcohol + 
                LabelAppeal + AcidIndex + STARS, data = m3train)
knitr::kable(summary(m2NBFit)$coefficients, digits = 3L,
             caption = 'Negative Binomial Regression Model #2 - Final Output')
```

#### Coefficient Discussion
The intercept of the final model tells us that there is typically ~1 case 
of wine purchased. Some things to note:

* Stars and label appeal contribute the most positively to the number of
cases of wine purchased. Intuitively, this makes sense - the higher the
rating and the prettier the bottle, the more cases we would expect to be
sold. 
* Free Sulfur Dioxide and Total Sulfur Dioxide have a very tiny effect on
the number of cases sold (rounded to 3 decimal places, the impact is 0!)
* All of the remaining variables except alcohol have a negative effect on 
the number of cases purchased.

### Multiple Linear Regrssion Model # 2
One drawback to traditional multiple linear regression models is that the 
forecasted counts are not integers. We will deal with this by rounding the
predictions to the nearest whole number.

#### Baseline Model
We will start with a simple linear model to serve as a baseline. This includes
all variables in the dataset.

```{r m2MLTrainBase}
m2MLBase <- lm(TARGET ~ ., data = m3train)
knitr::kable(summary(m2MLBase)$coefficients, digits = 3L,
             caption = 'Multiple Regression Model #2 - Base Output')
```
Most of the variables in the dataset are significant, but we can immediately
see a few that are above the 0.05 p-value threshold.

#### Enhanced Model
Backwards stepwise regression is performed and the result is a model with the 
following variables *removed*: `FixedAcidity`, `CitricAcid`, `ResidualSugar`, 
and `Density`.

```{r m2MLTrain}
m2MLFit <- lm(TARGET ~ VolatileAcidity + Chlorides + FreeSulfurDioxide 
              + TotalSulfurDioxide + pH + Sulphates + Alcohol + LabelAppeal 
              + AcidIndex + STARS, data = m3train)
knitr::kable(summary(m2MLFit)$coefficients, digits = 3L,
             caption = 'Multiple Regression Model #2 - Final Output')
```

#### Coefficient Discussion
The intercept of the final model tells us that there are typically ~3 cases 
of wine purchased. Some things to note:

* As expected, the number of stars has the largest, positive impact on the 
number of cases sold. This makes sense -- the higher the rating of a wine,
the more of it we would expect to be purchased. 
* Label appeal has the second largest impact on the number of cases sold. 
They say one shouldn't judge a book by its cover (or in this case, a wine
by its label), but it does appear to have quite a significant impact on
sales. 
* Alcohol also has a small positive impact on the number of cases purchased. 
This means that the more alcohol a wine has, the more cases of it will be
purchased. 
* Acid Index, Sulphates, pH, Chlorides, and VolatileAcidity all have a
negative impact on the number of cases sold.

@@

```{r m2TestProcess}
set.seed(525)
m2test <- copy(tstSet[,-1])
m2test[,c(2:8,11:12)] <- abs(m2test[,c(2:8,11:12)])
m2test$STARS[is.na(m2test$STARS)] <- 0
m2test.impute <- mice(m2test, method = 'pmm', print = FALSE)
m2test <- complete(m2test.impute)
m2test.r <- m2test$TARGET
m2test.p <- m2test[,-1]
pre.process <- preProcess(m2test.p, method = c("YeoJohnson"))
m2test.p <- predict(pre.process, m2test.p)
m2test[,c(2:13,15)] <- m2test.p[,c(1:12,14)]
```
```{r m2PTest}
# ZIP2: Test Model
m2PtstPred = round(predict(m2.fpmodel, newdata = m2test))
compTable[2, 2] <- m2PRMSE <- RMSE(m2PtstPred, m2test.r)
compTable[2, 3] <- m2PMAE <- MAE(m2PtstPred, m2test.r)
compTable[2, 4] <- m2.poisson.aic
```

**Poisson Model 2** has an RMSE of 
`r prettyNum(m2PRMSE, digits = 2L)`, an MAE of 
`r prettyNum(m2PMAE, digits = 2L)`, and a training AIC of 
`r prettyNum(m2.poisson.aic, digits = 2L)`.

### Negative Binomial Model 1

```{r m1NBTest}
# NB1: Test Model
m1NBtstPred <- round(predict(m1NBFit, newdata = m1tstImp))
compTable[3, 2] <- m1NBRMSE <- RMSE(m1NBtstPred, m1tstImp$TARGET)
compTable[3, 3] <- m1NBMAE <- MAE(m1NBtstPred, m1tstImp$TARGET)
compTable[3, 4] <- m1NBFitAIC 
```

@@

```{r m2NBTest}
# NB2: Test Model
m2NBtstPred <- round(predict(m2NBFit, newdata = m3test))
compTable[4, 2] <- m2NBRMSE <- RMSE(m2NBtstPred, m3test$TARGET)
compTable[4, 3] <- m2NBMAE <- MAE(m2NBtstPred, m3test$TARGET)
compTable[4, 4] <- m2NBFitAIC <- AIC(m2NBFit)
```

**Negative Binomial Model 2** has an RMSE of
`r prettyNum(m2NBRMSE, digits = 2L)`, an MAE of
`r prettyNum(m2NBMAE, digits = 2L)`, and a training AIC of
`r prettyNum(m2NBFitAIC, digits = 2L)`.

@@

```{r m1MLRTest}
# MLR1: Test Model
m1MLRtstPred <- round(predict(m1MLRFit, newdata = m2test))
compTable[5, 2] <- m1MLRRMSE <- RMSE(m1MLRtstPred, m2test.r)
compTable[5, 3] <- m1MLRMAE <- MAE(m1MLRtstPred, m2test.r)
compTable[5, 4] <- m1MLRFitAIC <- AIC(m1MLRFit)
```

**Multiple Linear Regression Model 2** has an RMSE of
`r prettyNum(m1MLRRMSE, digits = 2L)`, an MAE of
`r prettyNum(m1MLRMAE, digits = 2L)`, and a training AIC of
`r prettyNum(m1MLRFitAIC, digits = 2L)`.

@@

```{r m2MLTest}
# MLR2: Test Model
m2MLtstPred <- round(predict(m2MLFit, newdata = m3test))
compTable[6, 2] <- m2MLMSE <- RMSE(m2MLtstPred, m3test$TARGET)
compTable[6, 3] <- m2MLMAE <- MAE(m2MLtstPred, m3test$TARGET)
compTable[6, 4] <- m2MLFitAIC <- AIC(m2MLFit)
```

**Multiple Linear Regression Model 1** has an RMSE of
`r prettyNum(m2MLMSE, digits = 2L)`, an MAE of
`r prettyNum(m2MLMAE, digits = 2L)`, and a training AIC of
`r prettyNum(m2MLFitAIC, digits = 2L)`.

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
<!-- Assignment -->
```{r loadData}
```
<!-- Data Exploration -->
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
<!-- Data Preparation -->
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m2clean}
```
```{r model3impute}
```
<!-- Build Models -->
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
```{r m1PvarImp}
```
```{r m1NBTrain}
```
```{r m1NBTable}
```
```{r m1NBvarImp}
```
```{r m1PNB}
```
```{r m2poisson}
```
```{r m2PTable}
```
```{r m2PFitCheck}
```
```{r m1MLRFit}
```
```{r m1MLRTable}
```
```{r m2NBTrainBase}
```
```{r m2NBTrain}
```
```{r m2MLTrainBase}
```
```{r m2MLTrain}
```
<!-- Select Models -->
```{r compTable}
```
```{r m1TestProcess}
```
```{r m1PTest}
```
```{r m2TestProcess}
```
```{r m2PTest}
```
```{r m1NBTest}
```
```{r m2NBTest}
```
```{r m1MLRTest}
```
```{r m2MLTest}
```
<!-- Remaining Test sets go here -->
```{r modelTestResults}
```
